Convergence rate of MAP estimates \\ for the exponential family

### 2021-10-21 aistats.tex
Update erratum

\begin{important}
{\bf Erratum:} There was an error in our derivations. In the main text, we claimed that the log-partition of a Gaussian was not self-concordant. We will now prove that the opposite is true.
\end{important}

>>>>

\begin{important}
	{\bf Erratum:}  
	In the main text, we claimed that the log-partition of a Gaussian was not self-concordant. 
	There was an error in our derivations and we will now prove the opposite.
	However this does not change our story, and in particular our concern about the lack of results in the few sample regime remains valid.
\end{important}
